---
title: "LDA Topic Modeling in R"
output: html_notebook
---

Uses TM for text data pre-processing and topicmodels package. 


```{r}
setwd("/Users/aneesha/user2018/")
```

```{r}
library(tm)
library(SnowballC)
library(topicmodels)
```

```{r}
survey_responses_raw<-read.csv("surveyresponses.csv", stringsAsFactors = FALSE)
```

```{r}
# show column names
colnames(survey_responses_raw)
```
```{r}
# display a document
survey_responses_raw$documents[3]
```

```{r}
# Perform Character Encoding
survey_responses_raw$documents <- iconv(survey_responses_raw$documents, "latin1", "ASCII", sub="")
# Vectorize the documents
survey_responses <- Corpus(VectorSource(as.vector(survey_responses_raw$documents))) 

```

```{r}
# Text Pre-processing
# convert to lowercase
survey_responses <- tm_map(survey_responses, tolower)
# remove punctuation
survey_responses <- tm_map(survey_responses, removePunctuation)
# remove numbers
survey_responses <- tm_map(survey_responses, removeNumbers);
# remove stopwords
stopword <- c(stopwords('english'), "best");
survey_responses <- tm_map(survey_responses, removeWords, stopword)
survey_responses <- tm_map(survey_responses, stemDocument)
```

```{r}
# Create document term matrix
survey_Dtm <- DocumentTermMatrix(survey_responses, control = list(minWordLength = 2));
survey_Dtm2 <- removeSparseTerms(survey_Dtm, sparse=0.98)

# Find best starting value for the number of topics (k)

source("optimal_K.r")
control <- list(burnin = 500, iter = 1000, keep = 100)

## Determine Optimal Number of Topics
(k <- optimal_k(survey_Dtm2, 20, control = control))
```
```

```{r}
k = 12; #number of topics
SEED = 1234;

no_top_words = 6 #no of top words to show
no_top_documents = 6 #no top documents to show

# Run LDA
survey.lda <- LDA(survey_Dtm2, k, method="Gibbs", control=list(seed = SEED))

lda.topics <- as.matrix(topics(survey.lda, 6))
lda.terms <- terms(survey.lda, no_top_words)
lda.terms

# print both top words and top documents in a topic
for (topic_no in 1:k){
  print(paste("Topic", topic_no))
  print(lda.terms[,topic_no])
  docs_in_topic <- survey.lda@gamma[,topic_no]
  ordered_docs <- order(docs_in_topic, decreasing = TRUE)
  top_ordered_docs <- ordered_docs[1:no_top_documents]
  print(top_ordered_docs)
  for (doc in top_ordered_docs){
    print(survey_responses_raw$documents[doc])
  }
}

```







